---
title: "GCI Impact"
author: "David Ferreira Quaresma (david.quaresma@ccc.ufcg.edu.br)"
date: "october, 2019"
output: pdf_document
---

# Runtime experiments: GCI vs NOGCI
```{r echo=FALSE, results='hide', message=FALSE}
source("functions.R")
gci   = filter(read.al(paste("../experiment/results/",   "gci1", ".csv", sep="")), status == 200)
nogci = filter(read.al(paste("../experiment/results/", "nogci1", ".csv", sep="")), status == 200)
gci$response_time = gci$response_time / 1000000
gci$service_time = gci$body / 1000000
nogci$response_time = nogci$response_time / 1000000
nogci$service_time = nogci$body / 1000000
```

## Descrição
- [**script de execução dos experimentos**](https://github.com/dfquaresma/gci-faas-sim/blob/master/experiment/run.sh).
- Número de requisições: 5 mil, [**código**](https://github.com/dfquaresma/gci-faas-sim/blob/master/experiment/workload.go).
- Lógica de negócio da função: [**Redimencionamento de uma imagem**](https://github.com/dfquaresma/gci-faas-sim/blob/master/runtime/thumb-func/src/main/java/com/openfaas/function/Handler.java).
- Escala de redimencionamento: 0.1.
- Tamanho da imagem: 131kb.
- Comando executado para levantar a aplicação: entrypoint_port=8082 scale=0.1 image_url=http://s3.amazonaws.com/wallpapers2/wallpapers/images/000/000/408/thumb/375.jpg taskset 0x1 nice -20 nohup java -server -Xms445645k -Xmx445645k -XX:MaxHeapSize=445645k -XX:MaxMetaspaceSize=52429k -XX:ReservedCodeCacheSize=26214k -Xshare:on -XX:-TieredCompilation -XX:+UseSerialGC -Djava.net.preferIPv4Stack=true -XX:NewSize=392m -XX:MaxNewSize=392m -Xloggc:/home/ubuntu/gci-faas-sim/experiment/results/gci1-thumb-gc.log -Djvmtilib=/home/ubuntu/gci-faas-sim/gci-files/libgc.so -javaagent:/home/ubuntu/gci-faas-sim/gci-files/gciagent-0.1-jar-with-dependencies.jar=8500 -jar /home/ubuntu/gci-faas-sim/runtime/thumb-func/target/thumbnailator-server-maven-0.0.1-SNAPSHOT.jar >/home/ubuntu/gci-faas-sim/experiment/results/gci1-thumb-stdout.log 2>/home/ubuntu/gci-faas-sim/experiment/results/gci1-thumb-stderr.log & taskset 0x2 nice -20 /home/ubuntu/gci-faas-sim/gci-files/gci-proxy --port=8080 --target=127.0.0.1:8082 --gci_target=127.0.0.1:8500 --ygen=314572800 >/home/ubuntu/gci-faas-sim/experiment/results/gci1-proxy-stdout.log 2>/home/ubuntu/gci-faas-sim/experiment/results/gci1-proxy-stderr.log &

#### ECDF for response time
```{r  fig.width=15, fig.height=5, echo=FALSE}
graph_tail(gci$response_time, nogci$response_time, c("GCI", "NOGCI"), title="THUMBNAILATOR ECDF RESPONSE TIME", x_limit_sup=100)
```

#### ECDF for service time
```{r  fig.width=15, fig.height=5, echo=FALSE}
graph_tail(gci$service_time, nogci$service_time, c("GCI", "NOGCI"), title="THUMBNAILATOR ECDF SERVICE TIME", x_limit_sup=100)
```

#### summary table of confidence interval for response time, both in milliseconds
```{r  fig.width=15, fig.height=5, echo=FALSE}
summary_table(gci$response_time, "gci", nogci$response_time, "nogci")
```

#### GCI: comparing response time vs service time, both in milliseconds
```{r  fig.width=15, fig.height=5, echo=FALSE}
summary_table(gci$service_time, "gci.st", gci$response_time, "gci.rs")
```

#### NOGCI: comparing response time vs service time, both in milliseconds
```{r  fig.width=15, fig.height=5, echo=FALSE}
summary_table(nogci$service_time, "nogci.st", gci$response_time, "nogci.rt")
```

#### checking errors
```{r  fig.width=15, fig.height=5, echo=FALSE}
gci$diff = gci$response_time - gci$service_time
nogci$diff = nogci$response_time - nogci$service_time
cat("GCI   - number of response time values greater then its service time values: ", NROW(filter(gci, diff < 0)), "\n")
cat("NOGCI - number of response time values greater then its service time values: ", NROW(filter(nogci, diff < 0)), "\n")
```

#### comparing difference between response time and service time for GCI vs NOGCI
```{r  fig.width=15, fig.height=5, echo=FALSE}
summary_table(gci$diff, "gci.st", nogci$diff, "nogci.rt")
```

#### GCI: plot response time
```{r fig.width=10, fig.height=5, echo=FALSE}
plot(gci$response_time, ylab="response time", main="GCI")
```

#### NOGCI: plot response time
```{r fig.width=10, fig.height=5, echo=FALSE}
plot(nogci$response_time, ylab="response time", main="NOGCI")
```
